% SPDX-FileCopyrightText: Copyright (C) Nile Jocson <atraphaxia@gmail.com>
% SPDX-License-Identifier: MPL-2.0



\section{}
Solve the following word problems algebraically.

\subsection{}
\aproblem{
	Find 3 consecutive even numbers whose sum is 78.
}{
	&=
}

\subsection{}
\aproblem{
	If the length of each side of a square is increased by 2 units, the resulting square has an area that is
	16 units more than the area of the original square. Determine the dimensions of the original square.
}{
	&=
}

\subsection{}
\aproblem{
	Susan is 9 years older than Ivy. Four years ago, the sum of their ages was 17 years. In how many years will Susan turn 18?
}{
	&=
}

\subsection{}
\aproblem{
	Ray and Joyce leave a park at the same time in separate directions. Ray drives 6 kilometers home while Joyce drives 7 kilometers
	home. They arrive at the same time at their respective homes. If Ray drives 3 kilomteres per hour slower than Joyce, what are their
	average rates?
}{
	&=
}

\subsection{}
\aproblem{
	To exclusively rent a videoke room, a certain number of people have to pay equal amounts to a total of Php 720.00. If there were 3
	persons less, each person would then have to contribute Php 40.00 more. How many people were there originally?
}{
	&=
}

\subsection{}
\aproblem{
	The numerator of a positive fraction is 5 more than thrice its denominator. If 13 is added to the denominator and 9 is subtracted
	from the numerator, the resulting fraction is twice the reciprocal of the original number. Find the original fraction.
}{
	&=
}

\subsection{}
\aproblem{
	Two friends living 39 miles apart leave their homes at the same time on bicycles and travel towards each other. If one person
	averages 2 miles per hour more than the other and they meet in $\dfrac{3}{2}$ hours, what is each person's average cycling speed?
}{
	&=
}

\subsection{}
\aproblem{
	Bus A leaves a terminal at 12:00 noon while Bus B headed for the same destination leaves the same terminal 15 minutes later.
	After covering 75 kilometers, Bus B catches up to Bus A at 1:15 pm. Determine the speed of each bus.
}{
	&=
}

\subsection{}
\aproblem{
	One alloy contains 80\% gold (by weight) and another contains 55\% gold. How many grams of each alloy must be combined to
	make 40 grams of an alloy that is 70\% gold?
}{
	&=
}

\subsection{}
\aproblem{
	One acid solution is 60\% water and another acid solution is 40\% water. How many liters of each solution should be mixed
	to produce 90 liters of acid solution which is 52\% water?
}{
	&=
}

\subsection{}
\aproblem{
	A grocer wishes to mix two types of coffee beans. One costs Php 40.00 per kilogram and the other costs Php 60.00 per
	kilogram. How much of each type must be mixed to obtatin 50 kilograms of coffee that reasonably costs Php 55.00 per
	kilogram?
}{
	&=
}

\subsection{}
\aproblem{
	Wes invested a total of Php 120,000.00 in two accounts. One account earns 7\% annual interest while the other earns
	5\% annual interest. If a year after the investment, Wes earns Php 7,400.00, how much did he put in each account?
}{
	&=
}

\subsection{}
\aproblem{
	If a rowing team rows with the current, they can cover 16 miles in 2 hours. Against the current, they can cover
	10 miles in 4 hours. Find their rate of rowing in calm water and the rate of the current.
}{
	&=
}

\subsection{}
\aproblem{
	Mary can clean an office in 10 hours. Working together, John and Mary can clean the office in 7 hours. How long
	would it take for John to clean the office by himself?
}{
	&=
}

\subsection{}
\aproblem{
	An office has two photocopy machines. Machine A can photocopy 1000 pieces of a single file in 5 hours, while
	Machine B can photocopy 1000 pieces of the same file in 4 hours. How long will it take the two machines, both
	working together to photocopy 1600 pieces of a file?
}{
	&=
}

\subsection{}
\aproblem{
	A man can paint a room by himself in 8 hours while his son can paint the same room in 12 hours. The man works
	by himself for 3 hours and is then joined by his son. How many hours will it take them to finish painting?
}{
	&=
}

\subsection{}
\aproblem{
	A woman can do a certain job in 8 hours, while her daughter can do it in 12 hours. After the woman and the
	daughter worked for an hour, they were joined by the woman's son, and the three completed the job in three
	hours. How long would it take the son to finish the same job alone?
}{
	&=
}
