% SPDX-FileCopyrightText: Copyright (C) Nile Jocson <atraphaxia@gmail.com>
% SPDX-License-Identifier: MPL-2.0



\section{}
	Solve the following word problems algebraically.

	\subsection{}
		Find 3 consecutive even numbers whose sum is 78.
		\begin{align*}
			\intertext{Consecutive even numbers have an interval of 2. Let the
			first number be $x$.}
			x + (x + 2) + (x + 4) &= 78 \\
			3x + 6 &= 78 \\
			3x &= 72 \\
			x &= 24 \\
			\intertext{Find the other two numbers.}
			\intertext{\centering\fbox{The numbers are 24, 26, and 28.}}
		\end{align*}
		\hrule{}

	\subsection{}
		If the length of each side of a square is increased by 2 units, the resulting
		square has an area that is 16 units more than the area of the original square.
		Determine the dimensions of the original square.
		\begin{align*}
			\intertext{Let the side length be $x$.}
			{(x + 2)}^2 &= x^2 + 16 \\
			x^2 + 4x + 4 &= x^2 + 16 \\
			4x &= 12 \\
			x &= 3 \\
			\intertext{\centering\fbox{The side length of the original square is \qty{3}{\unit{u}}.}}
		\end{align*}
		\hrule{}

	\subsection{}
		Susan is 9 years older than Ivy. Four years ago, the sum of their ages was 17
		years. In how many years will Susan turn 18?
		\begin{align*}
			\intertext{Let Susan's age be $x$. Ivy's age is then $x - 9$. Four years ago,
			Susan and Ivy were $x - 4$ and $x - 13$ years old, respectively.}
			(x - 4) + (x - 13) &= 17 \\
			2x &= 34 \\
			x &= 17 \\
			\intertext{\centering\fbox{Susan will turn 18 in one year.}}
		\end{align*}

	\subsection{}
		Ray and Joyce leave a park at the same time in separate directions. Ray drives
		6 kilometers home while Joyce drives 7 kilometers home. They arrive at the same
		time at their respective homes. If Ray drives 3 kilometers per hour slower than
		Joyce, what are their average rates?
		\begin{align*}
			\intertext{We have $d = st$ or $t = \frac{d}{s}$. Let Joyce's speed be $x$.}
			\frac{6}{x - 3} &= \frac{7}{x} \\
			\intertext{$x \notin \{0, 3\}$} \\
			6x &= 7x - 21 \\
			x &= 21 \\
			\intertext{\centering\fbox{Ray drives at \qty{18}{\kilo\meter\per\hour} while Joyce drives at \qty{21}{\kilo\meter\per\hour}.}}
		\end{align*}
		\hrule{}

	\subsection{}
		To exclusively rent a videoke room, a certain number of people have to pay equal
		amounts to a total of Php 720.00. If there were 3 persons less, each person would
		then have to contribute Php 40.00 more. How many people were there originally?
		\begin{align*}
			\intertext{Let the original number of people be $x$.}
			\frac{720}{x} + 40 &= \frac{720}{x - 3} \\
			\intertext{$x \notin \{0, 3\}$}
			720(x - 3) + 40x(x - 3) &= 720x \\
			720x - 2160 + 40x^2 - 120x &= 720x \\
			40x^2 - 120x - 2160 &= 0 \\
			x^2 - 3x - 54 &= 0 \\
			(x - 9)(x + 6) &= 0 \\
			x &\in \{-6, 9\} \\
			\intertext{A negative amount of people doesn't make sense.}
			\intertext{\centering\fbox{There were 9 people originally.}}
		\end{align*}
		\pagebreak{}

	\subsection{}
		The numerator of a positive fraction is 5 more than thrice its denominator. If 13
		is added to the denominator and 9 is subtracted from the numerator, the resulting
		fraction is twice the reciprocal of the original number. Find the original fraction.
		\begin{align*}
			\intertext{Let the denominator of the original fraction be $x$. The original
			numerator is then $3x + 5$.}
			2{\left(\frac{3x + 5}{x}\right)}^{-1} &= \frac{3x - 4}{x + 13} \\
			\frac{2x}{3x + 5} &= \frac{3x - 4}{x + 13} \\
			\intertext{$x \notin \left\{-13, -\frac{5}{3}\right\}$}
			2x(x + 13) &= (3x + 5)(3x - 4) \\
			2x^2 + 26x &= 9x^2 + 3x - 20 \\
			7x^2 - 23x - 20 &= 0 \\
			x &= \frac{23 \pm \sqrt{{(-23)}^2 - 4(7)(-20)}}{2(7)} \\
			x &= \frac{23 \pm \sqrt{529 + 560}}{14} \\
			x &= \frac{23 \pm \sqrt{1089}}{14} \\
			x &= \frac{23 \pm 33}{14} \\
			x &\in \left\{\frac{56}{14}, -\frac{10}{14}\right\} \\
			x &\in \left\{4, -\frac{5}{7}\right\} \\
			\intertext{We want a positive fraction, so we need same signs for the numerator
			and denominator. Our numerator and denominator will both be positive if we use 4.}
			x &= 4 \\
			\intertext{\centering\fbox{The original fraction is $\frac{17}{4}$.}}
		\end{align*}
		\hrule{}

	\subsection{}
		Two friends living 39 miles apart leave their homes at the same time on bicycles
		and travel towards each other. If one person averages 2 miles per hour more than
		the other and the meet in $\frac{3}{2}$ hours, what is each person's average cycling
		speed?
		\begin{align*}
			\intertext{We have $d = st$. Let one of the cyclists' speed be $x$. Their total
			distance covered is 39 miles.}
			\frac{3}{2}x + \frac{3}{2}(x + 2) &= 39 \\
			3x + 3(x + 2) &= 78 \\
			2x + 2 &= 26 \\
			x &= 24 \\
			x &= 12 \\
			\intertext{\centering\fbox{Their speeds are \qty{12}{\unit{mph}} and \qty{14}{\unit{mph}}, respectively.}}
		\end{align*}
